### 2021-03-09 README.Rmd
added the DOI to the README
updated some references.
Added DOI info to the README page, now that the paper is published.

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models"
Authors <- "See, Kevin E., Michael W. Ackerman, Richard A. Carmichael, Sarah Hoffman, and Chris Beasley"
yr <- 2020
Journal <- "Ecosphere"
```

@@

@@

> `r Authors` (`r yr`). _`r Title`_. `r Journal` <https://doi.org/xxx/xxx>

Our pre-print is online here:

> `r Authors` (`r yr`). _`r Title`_. `r Journal`, Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

@@

> `r Authors`, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/xxx/xxx>

>>>>

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
# Please put your title here to include it in the file below.
Title <- "Estimating Carrying Capacity for Juvenile Salmon using Quantile Random Forest Models"
Authors <- "See, Kevin E., Michael W. Ackerman, Richard A. Carmichael, Sarah Hoffman, and Chris Beasley"
yr <- 2021
Journal <- "Ecosphere"
```

@@

[![DOI](https://zenodo.org/badge/225946308.svg)](https://zenodo.org/badge/latestdoi/225946308)

@@

> `r Authors` (`r yr`). _`r Title`_. `r Journal` <http://doi.org/10.1002/ecs2.3404 >

@@

> `r Authors`, (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for `r Title`_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.4300942>
